Toward dynamic models of combat or lack thereof in animal mating

### 2016-05-04 ms.tex
renamed data folder in remake.yml

\myfigure{figures/energy_pc_plot_cm_100.png}{pc energy spent on what}{figures/energy_total_plot_cm_100.png}{total energy spent on what}

\begin{figure}[h!]
    \centering
    \includegraphics[width=15cm,height=10cm]{figures/clustered_e_0_plot.pdf}
    \caption{A plot of the distribution of the aggression parameter $beta$ over varing $A_{total}$ with k means clustering done, with the k parameter chosen by $pamk$, the number of clusters (coexisting strategies) can be be seen on the right}
\end{figure}

>>>>

%\myfigure{figures/energy_pc_plot_fixed_r_v.png}{pc energy spent on what}{figures/energy_total_plot_fixed_r_v.png}{total energy spent on what, fixed r_v}

\begin{figure}[h!]
    \centering
    \includegraphics[width=15cm,height=10cm]{figures/clustered_e_0_plot.pdf}
    \caption{A plot of the distribution of the aggression parameter $beta$ over varing $A_{total}$ with k means clustering done, with the k parameter chosen by $pamk$, the number of clusters (coexisting strategies) can be be seen on the right, r - v fixed}
\end{figure}
